\begin{enumerate}

\item If $4 \cot^{2}45\degree-\sec^{2}60\degree+\sin^{2}60\degree+p=\frac{3}{4},$ then find the value of p.

\item If $\cos A$ + $\cos^{2}A = 1$ ,then find the value of $\sin^{2}A$ + $\sin^{4}A$

\item The length of the shadow of a tower on the plane ground is $ \sqrt3 $ times the height of the tower. Find the angle of elevation of the sun.

\item The angle of elevation of the top of a tower from a point on the ground which is $30 \mathrm{m}$ away from the foot of the tower,is $30\degree$.Find the height of the tower.

\item Prove that :
\begin{align}
	\brak{\frac{1}{\cos\theta}-\cos\theta} \brak{\frac{1}{\sin\theta}-\sin\theta} = \frac{1}{\tan\theta + \cot\theta}
\end{align}

\item As observed from the top of a $75 \mathrm{m}$ high lighthouse from the sea-level, the angles of depression of two ships are $30\degree$ and $60\degree$. If one ship is exactly behind the other on the same side of the lighthouse, find the distance between the two ships.\\
	$\brak{Use \sqrt{3} = 1.73}$

\item From a point on the ground, the angle of elevation of the bottom and top of a transmission tower fixed at the top of $30 \mathrm{m}$ high building are $30\degree$ and $60\degree$, respectively. Find the height of the transmission tower. $\brak{Use\sqrt{3} = 1.73}$.
	\item If a pole 6 m high casts a shadow $2 \times \sqrt{3}$m long on the ground,then sun's elevation is:
	\begin{enumerate}
	\item $60\degree$
	\item $45\degree$
	\item $30\degree$
	\item $90\degree$
	\end{enumerate}
 \item $ (\sec^2 \theta - 1)(\cosec^2 \theta - 1)$
is equal to:
\begin{enumerate}
	\item $-1$
	\item $1$
	\item $0$
	\item $2$
\end{enumerate}

\item
Evaluate \begin{align}
2\sec^2\theta + 3\csc^2\theta - 2\sin\theta\cos\theta  \ \text{if} \ \theta = 45\degree.
\end{align}
\item 
If \begin{align} 
\sin\theta - \cos\theta = 0, \text{ then find the value of }\sin^4\theta + \cos^4\theta.
\end{align}
\item
Prove that \begin{align} \frac{\sin{A}-2sin^3{A}}{2\cos^3{A}-\cos{A}}=\tan{A} \end{align}
\item
Prove that \begin{align} \sec{A\brak{1-\sin{A}}\brak{\sec{A}+\tan{A}}}=1. \end{align}
\item
	A straight highway leads to the foot of a tower. A man standing on the top of the $75 \mathrm{m}$ high tower observes two cars at angles of depression of $30^\circ$ and $60^\circ$, which are approaching the foot of the tower. If one car is exactky behind the other on the same side of the tower, fin
d the dist
ance between the two cars. use \brak{\sqrt{3}=1.73}.
\item
	From the top of a $7 \mathrm{m}$ building, the angle of elevation of the top a cable tower is 60\degree and the angle of depression of its foot is 30\degree. Determine the height of the tower.

\end{enumerate}

